wind_diagrams

### 2019-12-16 wind_analyses.Rmd
progress

```{r}

>>>>

```{r}
match_funcs <- function(df){
  unique_pixel <- df %>%
    select(lon, lat) %>%
    unique()
}

match_OISST <- match_funcs(df = OISST)
match_CMC <- match_funcs(df = CMC)

# # Select 1 nearest pixel (k = 1)
# # here we ue knnx to find the closes pixel to the insitu sites
match_index_func <- function(df){
  match_index <- knnx.index(data = as.matrix(df[,1:2]),
                            query = as.matrix(site_list_sub[,5:6]), k = 1)
}

match_index_OISST <- match_funcs(df = match_OISST)
match_index_CMC <- match_funcs(df = match_CMC)

# # Select SST pixels nearest to insitu sites

pixel_match_OISST <- match_OISST[match_index_OISST,] %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>% 
  mutate(site = site_list_sub$site)

pixel_match_CMC <- match_OISST[match_index_CMC,] %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>% 
  mutate(site = site_list_sub$site)
